\documentclass[a4paper,10pt]{rewrite}
\pagenumbering{gobble}

% title formats
\titleformat{\section}
  {\normalfont\bfseries\large}{}{0pt}
  {\textcolor{sectioncolor}{#1}}
\titlespacing*\section{0pt}{5pt}{5pt}

\titleformat{\subsection}
  {\normalfont\bfseries\small}{}{0pt}
  {\textcolor{sectioncolor}{#1}}
\titlespacing*\subsection{0pt}{10pt}{5pt}

\newcommand{\smallbullet}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2}\end{picture}\ }
\newcommand{\sbt}{\smallbullet\ }

% begin document  
\begin{document}
\RaggedRight

% title
\titlesectionnew{Sundeep Routhu}
{+1 (857) 492-2030}
{routhusundeep@gmail.com}
{linkedin.com/in/sundeep-routhu} 
{github.com/routhusundeep}

\begin{center}
\textit{Software Engineer with 8 years building high-scale backend systems and distributed infrastructure serving millions of users.}
\end{center}

% Work Experience Section
\section*{Work Experience}
\subsection*{\workentrynew{Grab}{Senior Software Engineer}{Singapore}{July 2022--July 2024}}
\begin{itemize}[left=0pt, itemsep=0pt, label=$\bullet$]
    \item Built end-to-end authentication system from scratch in Go on AWS, including custom OAuth 2.1 implementation, handling \textasciitilde10M peak daily logins across countries and applications (rides, food, payments).
    \item Reduced login drop-off from 5\% to 2\% by optimizing authentication flows and adopting security best practices, enabling thousands of additional successful logins daily and driving revenue growth.
    \item Implemented multi-factor authentication from the ground up, supporting push-based MFA and social logins, saving up to \textasciitilde\$200k annually in SMS costs while enhancing security and preventing fraudulent logins.
    \item Architected family account grouping system as technical point of contact across payments, profile, and product teams, enabling secure sharing of payment methods and rides.
    \item Deployed Redis Bloom filter to eliminate invalid session lookups, improving P99.99 authentication latency from 1s to 400ms.
\end{itemize}

\subsection*{\workentrynew{VISA}{Senior Software Engineer}{Singapore}{Jan 2019--Jun 2022}}
\begin{itemize}[left=0pt, itemsep=0pt, label=$\bullet$]
    \item Developed cardholder benefits platform for hundreds of banks processing benefit eligibility for 900M cards daily, enabling personalized rewards based on spending patterns.
    \item Designed configurable rules engine for benefit personalization based on card types, merchant categories, tiered spend thresholds, and cross-border transactions.
    \item Architected 1TB/day pipeline migration to Hadoop/Spark/Kafka/Hive, leading 3 engineers and 2 QA to cut processing from 4hrs to 20min and save ~\$100k annually in licensing. Implemented staged migration with atomic batching, with data models adopted by 7 downstream services.
    \item Independently maintained full-stack Java/Spring + TypeScript web app for benefit redemption, serving hundreds of thousands of customers.
\end{itemize}

\subsection*{\workentrynew{Works Applications}{Software Engineer}{Singapore}{Oct 2016--Dec 2018}}
\begin{itemize}[left=0pt, itemsep=0pt, label=$\bullet$]
    \item Created framework generalizing journal entry creation across enterprise applications for hundreds of Japanese companies, supporting diverse expense types (rides, meals, travel, insurance).
    \item Migrated a monolithic system to event-driven microservices, reducing mean response time from 800ms to 250ms while improving scalability and fault tolerance.
\end{itemize}

% Projects Section
\section*{Projects}
\begin{itemize}[left=0pt, itemsep=0pt, label=$\bullet$]
    \item \textbf{\textcolor{titlecolor}{In-Context Learning in LLMs:}} Studying how context examples influence autoregressive, seq2seq, and instruction-tuned LLMs, analyzing how input and label distributions impact model accuracy and generalization.
    \item \textbf{\textcolor{titlecolor}{Consensus Protocols:}} Implemented \href{https://github.com/routhusundeep/paxos}{Multi-Paxos} and \href{https://github.com/routhusundeep/raft}{Raft} in Rust with leader election, log replication, and automatic recovery. Built sharded key-value store in Go using \href{https://github.com/routhusundeep/omnipaxos-go}{Omni-Paxos} for fault-tolerant replication.
    \item \textbf{\textcolor{titlecolor}{What I Learned:}} Maintaining a \href{https://github.com/routhusundeep/What-I-Learned}{GitHub repository} of notes and interpretations on distributed systems and datastore research papers.
\end{itemize}

% Skills Section
\section*{Skills}
\begin{itemize}[left=0pt, itemsep=0pt, label=\textcolor{titlecolor}{$\bullet$}]
    \item \textbf{\textcolor{titlecolor}{Languages:}} C/C++, Java, Rust, Go, Haskell, Python, SQL
    \item \textbf{\textcolor{titlecolor}{Data \& Infrastructure:}} AWS (Lambda, DynamoDB, Kinesis, EC2, ALB, Cognito), Spark, Hadoop, Hive, Kafka, Flink, Redis, Cassandra, HBase, PostgreSQL, MongoDB, ElasticSearch, Jenkins, Terraform, Airflow, Kubernetes
    \item \textbf{\textcolor{titlecolor}{Tools \& Protocols:}} Prometheus, Grafana, Kong, gRPC, GraphQL, REST
\end{itemize}

% Education Section
\section*{Education}
\begin{itemize}[left=0pt, itemsep=0pt, label=$\bullet$]
    \item \textbf{B.Tech. in Computer Science}, Indian Institute of Technology Bombay, 2012--2016 (All India Rank: 43)
    \item \textbf{M.Sc. in Computer Science}, Boston University (expected 2025)
\end{itemize}

\end{document}